<!-- Fig. 6: Validity -->

```{r scale function{{z}}-1, message=FALSE, echo=FALSE}
# function that sets limits of the scale (for all plots)
set_breaks = function(limits) {
     seq(limits[1], limits[2], by = 1)
}
```

<table style="width: 100%; border-collapse: collapse; border: 1px solid grey; text-align: center;">
  <colgroup>
    <col span="1" style="background-color:lightgrey; border: 1px solid grey;">
    <col span="2" style="border: 1px solid grey;">
  </colgroup>
  <tr style="background-color:lightgrey; border: 1px solid grey;">
    <td></td>
    <td>**for Accuracy Data**<br>**_without_ Process Data**</td>
    <td>**for Accuracy Data**<br>**_with_ Process Data**</td>
    <td>**for Accuracy Data**<br>**_with_ Process Data**<br>**_excl._ dropped tasks**</td>
  </tr>
  <tr style="border: 1px solid grey;">
    <td>**Only Location Tasks**</td>
    <td>`r format(round(cor_valid_loc_r,2), nsmall=2)`<br>
    <i>`r signif(cor_valid_loc_r_p,digits=3)`</i>
```{r plot validation correlation{{z}}-1, message=FALSE, echo=FALSE}
ggplot(data = totalscore, aes(x = sumloc_r, y = expertscoring)) +
   geom_count(color='black', ) +
   geom_smooth(method='lm', color='#3880ff', formula = y ~ x) +
   xlab("OriGami NMR Test Scoring") +
   ylab("Expert Scoring") +
   scale_size_continuous(breaks = set_breaks, range = c(2,3))
```
    </td>
    <td>`r format(round(cor_valid_loc_c,2), nsmall=2)`<br>
    <i>`r signif(cor_valid_loc_c_p,digits=3)`</i>
```{r plot validation correlation{{z}}-4, message=FALSE, echo=FALSE}
ggplot(data = totalscore, aes(x = sumloc_c, y = expertscoring)) +
  geom_count(color='black') + 
  geom_smooth(method='lm', color='#3880ff', formula = y ~ x) +
  xlab("OriGami NMR Test Scoring") + 
  ylab("Expert Scoring") +
  scale_size_continuous(breaks = set_breaks, range = c(2,3))
```
    </td>
    <td>`r format(round(cor_valid_loc_c_drop,2), nsmall=2)`<br>
    <i>`r signif(cor_valid_loc_c_drop_p,digits=3)`</i>
```{r plot validation correlation{{z}}-7, message=FALSE, echo=FALSE}
ggplot(data = totalscore_drop, aes(x = sumloc_c, y = expertscoring)) +
  geom_count(color='black') + 
  geom_smooth(method='lm', color='#3880ff', formula = y ~ x) +
  xlab("OriGami NMR Test Scoring") + 
  ylab("Expert Scoring") +
  scale_size_continuous(breaks = set_breaks, range = c(2,3))
```
    </td>
  </tr>
  <tr style="border: 1px solid grey;">
    <td>**All Tasks**</td>
    <td>`r format(round(cor_valid_total_r,2), nsmall=2)`<br>
    <i>`r signif(cor_valid_total_r_p,digits=3)`</i>
```{r plot validation correlation{{z}}-3, message=FALSE, echo=FALSE}
ggplot(data = totalscore, aes(x = sumtotal_r, y = expertscoring)) +
  geom_count(color='black') + 
  geom_smooth(method='lm', color='#3880ff', formula = y ~ x) +
  xlab("OriGami NMR Test Scoring") + 
  ylab("Expert Scoring") +
  scale_size_continuous(breaks = set_breaks, range = c(2,3))
```
    </td>
    <td>`r format(round(cor_valid_total_c,2), nsmall=2)`<br>
    <i>`r signif(cor_valid_total_c_p,digits=3)`</i>
```{r plot validation correlation{{z}}-6, message=FALSE, echo=FALSE}
ggplot(data = totalscore, aes(x = sumtotal_c, y = expertscoring)) +
  geom_count(color='black') + 
  geom_smooth(method='lm', color='#3880ff', formula = y ~ x) +
  xlab("OriGami NMR Test Scoring") + 
  ylab("Expert Scoring") +
  scale_size_continuous(breaks = set_breaks, range = c(2,3))
```
    </td>
    <td>`r format(round(cor_valid_total_c_drop,2), nsmall=2)`<br>
    <i>`r signif(cor_valid_total_c_drop_p,digits=3)`</i>
```{r plot validation correlation{{z}}-9, message=FALSE, echo=FALSE}
ggplot(data = totalscore_drop, aes(x = sumtotal_c, y = expertscoring)) +
  geom_count(color='black') + 
  geom_smooth(method='lm', color='#3880ff', formula = y ~ x) +
  xlab("OriGami NMR Test Scoring") + 
  ylab("Expert Scoring") +
  scale_size_continuous(breaks = set_breaks, range = c(2,3))
```
    </td>
  </tr>
</table>