#### Score Distribution

In the following, the distribution of the NMR competency score for `r location` is presented.

```{r calculate totalscores{{z}}, echo=FALSE}
source("calculations/3_testeval_scoredistrib_validity/01_totalscores.R", local = knitr::knit_global())
```

```{r fig5{{z}}, echo = FALSE}
src <- lapply(z, function(z) knitr::knit_expand(file = "tables_and_figures/fig05_totalscore_distribution.Rmd"))
```
`r knitr::knit(text = unlist(src))`
_Fig. `r 5 - figmin` - `r location`: Total Score Distribution._

The total scoring data can be found in the files `scoring.Rda` or `scoring.json` of the `results` folder.

#### Validity

The test validity is determined by correlating the score with the expert judgment, which is visualized in the following.

```{r calculate validity{{z}}, echo=FALSE}
source("calculations/3_testeval_scoredistrib_validity/02_validity.R", local = knitr::knit_global())
```

```{r fig6{{z}}, echo = FALSE}
src <- lapply(z, function(z) knitr::knit_expand(file = "tables_and_figures/fig06_validity.Rmd"))
```
`r knitr::knit(text = unlist(src))`
_Fig. `r 6 - figmin` - `r location`: Validity Coefficients with p-values in brackets._

```{r store data files 2{{z}}, echo = FALSE}

if(location=="Senden"){
  save(totalscore,file="results/senden/totalscore.Rda")
  write_json(totalscore,"results/senden/totalscore.json")
} else {
  if(location=="Duelmen"){
    save(totalscore,file="results/duelmen/totalscore.Rda")
    write_json(totalscore,"results/duelmen/totalscore.json")
  } else {
      save(totalscore,file="results/custom/totalscore.Rda")
      write_json(totalscore,"results/custom/totalscore.json")
  }
}
```