In the following, the reader can manipulate the _thresholds_ (chapter 2.2.4) manually in order to see their effects on the assessment evaluation (reliability and validity). The thresholds describe the "line" between a user's correct and incorrect as well as a certain and uncertain task solution. The colors and symbols of the boxes visualize the test evaluation. Additionally, with the file `SensAnalysis_ParameterOpt.R` in this R project, the reader has access to the calculations on all possible evaluation results which can be achieved in the sensitivity analysis for all combinations of the thresholds in a certain range.

```{r sensitivity analysis ui d, echo = FALSE}
ui_d <- dashboardPage(
  dashboardHeader(disable=TRUE),
  dashboardSidebar(disable=TRUE),
  
  dashboardBody(
    
    tags$head(tags$style(HTML('.content-wrapper, .right-side {background-color: #ffffff;}'))),
        
    fluidPage(
      
      # menu
      
      fluidRow(
        
        column(width=4,
          box(title = "Self-Location", width = 12, solidHeader = FALSE, status = "primary",
            fluidPage(
              sliderInput("loc", label = "Deviation (m):", min = 5, max = 20, value = LOClimit),
              sliderInput("locpan", label = "Number of Pannings:", min = 5, max = 40, value = locpanlimit),
              sliderInput("loczoom", label = "Number of Zoomings:", min = 5, max = 40, value = loczoomlimit),
            ),
          ),
        ),
        
        column(width=4,
          box(title = "Location", width = 12, solidHeader = FALSE, status = "success",
            selectInput("location", label = "Choose:", choices = c("Senden","Duelmen"), selected = "Senden"),
          ),
          box(title = "Navigation-to-a-Flag", width = 12, solidHeader = FALSE, status = "primary",
            fluidPage(
              sliderInput("lnv", label = "Deviation (m):", min = 5, max = 20, value = LNVlimit),
              sliderInput("lnvroute", label = "Factor of shortest route:", min = 2, max = 5, value = lnvroutefactor, step = 0.1),
            ),
          ),     
        ),
        
        column(width=4,
          box(title = "Mark-View-Direction", width = 12, solidHeader = FALSE, status = "primary",
            fluidPage(
              sliderInput("dm", label = "Deviation (°):", min = 5, max = 30, value = DMlimit),
            ),
          ),
          box(title = "Adopt-View-Direction", width = 12, solidHeader = FALSE,  status = "primary",
            fluidPage(
              sliderInput("da", label = "Deviation (°):", min = 5, max = 30, value = DAlimit),
              sliderInput("daturn", label = "Sum of Turnings (°):", min = 200, max = 1200, value = daturnlimit, step = 10),
            ),
          ),
        ),
        
    ),
    
    # boxes
    
    fluidRow(
      
      valueBoxOutput("reliability_l"),
      valueBoxOutput("reliability_all"),
      valueBoxOutput("reliability_all_drop"),
      valueBoxOutput("validity_l"),
      valueBoxOutput("validity_all"),
      valueBoxOutput("validity_all_drop"),

    ),
  
    )
  )
)
```

```{r sensitivity analysis server d, echo=FALSE}
source("calculations/4_testeval_sensanalysis/02_sensanalysis_valbox.R", local = knitr::knit_global())

server_d <- function(input, output) {
  
  output$reliability_l <- renderValueBox({
    source("calculations/4_testeval_sensanalysis/01_sensanalysis_code.R", encoding="utf-8", local = TRUE)
    valueBox(
      format(round(rel_Lc,2), nsmall=2), 
      "Reliability (Location Tasks)",
      icon = icon(valueboxicon(x=rel_Lc), lib = "font-awesome"),
      color = valueboxcolor(x=rel_Lc)
    )
  })
  
  output$reliability_all <- renderValueBox({
    source("calculations/4_testeval_sensanalysis/01_sensanalysis_code.R", encoding="utf-8", local = TRUE)
    valueBox(
      format(round(rel_Totalc,2), nsmall=2), 
      "Reliability (All Tasks)",
      icon = icon(valueboxicon(x=rel_Totalc), lib = "font-awesome"),
      color = valueboxcolor(x=rel_Totalc)
    )
  })
  
  output$reliability_all_drop <- renderValueBox({
    source("calculations/4_testeval_sensanalysis/01_sensanalysis_code.R", encoding="utf-8", local = TRUE)
    valueBox(
      format(round(rel_Totalc_drop,2), nsmall=2), 
      "Reliability (All Tasks; dropped)",
      icon = icon(valueboxicon(x=rel_Totalc_drop), lib = "font-awesome"),
      color = valueboxcolor(x=rel_Totalc_drop)
    )
  })
    
  output$validity_l <- renderValueBox({
    source("calculations/4_testeval_sensanalysis/01_sensanalysis_code.R", encoding="utf-8", local = TRUE)
    valueBox(
      format(round(cor_valid_loc_c,2), nsmall=2), 
      "Validity (Location Tasks)",
      icon = icon(valueboxicon(x=cor_valid_loc_c), lib = "font-awesome"),
      color = valueboxcolor(x=cor_valid_loc_c)
    )
  })
  
  output$validity_all <- renderValueBox({
    source("calculations/4_testeval_sensanalysis/01_sensanalysis_code.R", encoding="utf-8", local = TRUE)
    valueBox(
      format(round(cor_valid_total_c,2), nsmall=2), 
      "Validity (All Tasks)",
      icon = icon(valueboxicon(x=cor_valid_total_c), lib = "font-awesome"),
      color = valueboxcolor(x=cor_valid_total_c)
    )
  })
  
  output$validity_all_drop <- renderValueBox({
    source("calculations/4_testeval_sensanalysis/01_sensanalysis_code.R", encoding="utf-8", local = TRUE)
    valueBox(
      format(round(cor_valid_total_c_drop,2), nsmall=2), 
      "Validity (All Tasks; dropped)",
      icon = icon(valueboxicon(x=cor_valid_total_c_drop), lib = "font-awesome"),
      color = valueboxcolor(x=cor_valid_total_c_drop)
    )
  })

}

shinyApp(ui_d, server_d, options = list(height = 800))
```
